### 2017-05-22 doc/categories.tex
Ridge plot.

\begin{enumerate}
	\item {\sc LR word}: word type
	\item {\sc LR deprel}: word type, dependency label and their interaction 
	\item {\sc LR position}: word type, position (binned as first, second, third, middle,
	antepenult, penult, last) and their interaction
	\item {\sc LR full}: word type, dependency label, position, word:dependency interaction, 
	word:position interaction
\end{enumerate}

@@

\begin{figure}
\centering
  \includegraphics[scale=0.35]{omission-stat/position-new.png}
\caption{Proportion of variance in omission scores explained by the
  linear regression models
 for {\sc Sum}, {\sc Visual} and {\sc Textual} pathways, relative to
 regressing on word identity only. }
\label{fig:rsquared}
\end{figure}

>>>>

\begin{enumerate}
	\item {\sc LR word}: word type
	\item {\sc LR dep}: word type, dependency label and their interaction 
	\item {\sc LR position}: word type, position (binned as {\sc first, second, third, middle,
	antepenult, penult, last}) and their interaction
	\item {\sc LR full}: word type, dependency label, position, word:dependency interaction, 
	word:position interaction
\end{enumerate}

@@

\begin{figure}
\centering
  \includegraphics[scale=0.35]{position-new.png}
\caption{Proportion of variance in omission scores explained by the
  linear regression models
 for {\sc Sum}, {\sc Visual} and {\sc Textual} pathways, relative to
 regressing on word identity and position only. }
\label{fig:rsquared}
\end{figure}
